---
title: "IMporting and Managing Financial Data"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

Importing and Managing Financial Data in R

# quantmod
getSymbols imports data from various sources into your workspace

src (source) options
Yahoo Finance - "yahoo"
Google Finance - "google"
FRED (Federal Reserve Bank of St. Louis) - "FRED"
Oanda (exchange rate) - "oanda"
csv files
```{r}
library(quantmod)

# output data as an xts object
# src tells the source
getSymbols(Symbols = "AAPL", src = "yahoo")

# if you want to assign the object yourself
getSymbols(Symbols = "AAPL", src = "yahoo", auto.assign = FALSE)
```

Returns xts object as default

# Quandl 

Data service to find data
www.quandl.com

Can choose the data object you want to return (dataframe, xts, time series, etc.)

Types of data output
"raw" (dataframe)
"ts" (time-series object froms stats package)
"zoo"
"xts"
"timeseries" 
```{r}
library(Quandl)
Quandl(code = "FRED/DGS10", type = "raw")
```

Can google specific things on the the web

Yahoo finance page
Look at the specific Symbol - this is in parenthesis after the name
There has to be a download data link for GetSymbols to download

Example looking at the Pfizer stock

```{r}
# Create an object containing the Pfizer ticker symbol
symbol <- "PFE"

# Use getSymbols to import the data
getSymbols(symbol, src = "yahoo")

# Look at the first few rows of data
head(PFE)
```

Example looking at Oanda exchange rate data
Oanda only provides 180 days of historical data