---
title: "Intro_to_purrr"
output: html_document
---



Foundations of Functional Programming with purrr
```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

Read in multiple files
```{r}
files <- list.files()

map(files, read_csv)
```

Find the sum of each elemen of the bird_counts sum list

Maybe the object must be a list?
```{r}
map(bird_counts, sum)
```

The function `map` iterates over a list

`map` traditionally outputs a list

This 
```{r}
map(survey_data, ~nrow(.x))
```

This will output a vector of numbers
```{r}
map_dbl(survey_data, ~nrow(.x))
```

This will output a vector of logicals
```{r}
map_lgl(survey_data, ~nrow(.x) == 14)
```

This will outputs a vector of characters - it will pull out the species names from a list
```{r}
map_chr(species_names, ~.x)
```

This will output a data frame
```{r}
suvey_rows <- data.frame(names = names(survey_data), rows = NA)

survey_rows$rows <- map_dbl(survey_data, ~nrow(.x))

survey_rows 
```

This outputs a list with the name of each movie as the list and the length inside the list
The outputs are the same, but the second is better syntax to use - the .x denotes where the list element goes in the function, when we use ".x" we also have to put a "~" infront of the function
```{r}
map(wesanderson, length)
map(wesanderson, ~length(x))
```


This outputs a dataframe with the number of colors as a column and the rownames as the wesanderson list
```{r}
data.frame(numcolors = map_dbl(wesanderson, ~length(.x)))
```

# Safely, Possibly, and Walk

Can use the function `safely` to show you where errors occurred - when we pipe it into transpose, it will show where the error occurred, first

Replace anything with an error with NA

```{r}
list(-10, 1, 10, 0) %>% 
      map(safely(log, otherwise = NA_real_)) %>%
    # Transpose the result
      transpose()
```

pull out the height element and convert from inches to cm

```{r}
height_ft <- map(sw_people ,"height") %>% 
  map(safely(function(x){
    x * 0.0328084
  }, quiet = FALSE)) %>% 
transpose()
```

replace safely with possibly  - this will out put just the data and not the error messages


```{r}
list(-10, 1, 10, 0) %>% 
      map(safely(function(x) {
log(x)
}
, otherwise = NA_real_)) 
```

use walk() to make lists easier to read - removes double bracketing and makes data more compact


```{r}
Short_list <- list(-10, 1, 10)

Short_list

walk(short_list, print)
```

for plots, you can plot multiple iterations using the map function


```{r}
# Load the gap_split data
data(gap_split)

# Map over the first 10 elements of gap_split
plots <- map2(gap_split[1:10], 
              names(gap_split[1:10]), 
              ~ ggplot(.x, aes(year, lifeExp)) + 
                geom_line() +
                labs(title = "Gap Split"))

# Object name, then function name
walk(plots, print)
```


Check if the list has names
```{r}
names(sw_films)

# if no names, then can use 

sw_films <- sw_films %>%
  set_names(map_chr(sw_films, "title"))
```

These do the same thing
```{r}
# Name gh_users with the names of the users
gh_users_named <- gh_users %>% 
    set_names(map_chr(gh_users, "name"))

# Check gh_repos structure
str(gh_repos)

# Name gh_repos with the names of the repo owner
gh_repos_named <- gh_repos %>% 
    map_chr(~ .[[1]]$owner$login) %>% 
    set_names(gh_repos, .)
```


Sort and try to ask a quesiton
```{r}
# Determine who joined github first
map_chr(gh_users, ~.x[["created_at"]]) %>%
      set_names(map_chr(gh_users, "name")) %>%
    sort()
```

GGplot and dataframes

Pull out data to create 4 columns
```{r}
map_df(gh_users, `[`, 
       c("login","name","followers","public_repos")) 
```

Pull out the title and character names and plot height of characters by film
```{r}
# Turn data into correct dataframe format
film_by_character <- tibble(filmtitle = map_chr(sw_films, "title")) %>%
    mutate(filmtitle, characters = map(sw_films, "characters")) %>%
    unnest()

# Pull out elements from sw_people
sw_characters <- map_df(sw_people, `[`, c("height", "mass", "name", "url"))

# Join the two new objects
character_data <- inner_join(film_by_character, sw_characters, by = c("characters" = "url")) %>%
    # Make sure the columns are numbers
    mutate(height = as.numeric(height), mass = as.numeric(mass))

# Plot the heights, faceted by film title
ggplot(character_data, aes(x = height)) +
  geom_histogram(stat = "count") +
  facet_wrap(~ filmtitle)
```


# Intermediate Functional Programming with purrr

```{r}
# we can use .x to refer to the first list and .y to refer to the second list
map2(visits2016, visits2017, ~.x + .y)

# this will do the same as above
map2(visits2016, visits2017, ~..1 + ..2)

# with more than 2 parameters
pmap(list, ~..1 + ..2 + ..3)
```

You can use `as_mapper` to create lambda functions (basically functions that are not named)

```{r}
# these do the exact same thing, but the second is shorter to write
round_mean <- function(x) {
  round(mean(x))
}

round_mean <- as_mapper(~ round(mean(.x)))
```


Name lists
```{r}
month.abb <- c("Jan", "Feb", "Mar")

all_visits <- list(visits2015, visits2016)

map(all_visits, ~set_names(.x, month.abb))

```

Can use the `keep` function to extract elements that satisfy a condition (with a TRUE/FALSE)

```{r}
# which month has received more than3000 visits
over_3000 <- keep(visits2016, ~sum(.x) > 3000)

names(over_3000)

# or

limits <- as_mapper(~sum(.x) >3000)

over_mapper(visits2016, limit)

names(over_mapper)
```

or can use `discard` to remove elements that satisfy a condition

Only keep parts that are factors 
```{r}
df_list <- list(iris, airquality) %>%
  map(head)

map(df_list, ~keep(.x, is.factor))
```

Predicates
Basically means TRUE/FALSE data

can use `every` function: does every element satisfy a condition?

can use `some` function: do some of the elements satisfy a condition
```{r}
every(visits2016, is.numeric)
# output is TRUE

# is the mean of every month above 1000?
every(visits2016, ~mean(.x) > 1000)
# output is FALSE

# is the mean of some of the months above 1000?
some(visits2016, ~mean(.x) > 1000)
# output is TRUE
```

`detect_index` will tell us the first element that satisfies a condition

```{r}
detect_index(visits2016, ~mean(.x) > 1000)
```

`detect` will show the actual elements (the values) 
```{r}
detect(visits2016, ~mean(.x) > 1000, .right = TRUE)
```

`has_element` will show if one element has a value of interest
```{r}
visits2016_mean <- map(visits2016, mean)

# does one of the means = 981?
has_element(visits2016_mean, 981)
# output is: TRUE
```


```{r}
# Create a threshold variable, set it to 160
threshold <- 160

# Create a mapper that tests if .x is over the defined threshold
over_threshold <- as_mapper(~ .x > threshold)

# Are all elements in every all_visits vectors over the defined threshold? 
map(all_visits, ~ every(.x, over_threshold))

# Are some elements in every all_visits vectors over the defined threshold? 
map(all_visits, ~ some(.x, over_threshold))
```

