---
title: "interview practice"
output: html_document
---

Questions: https://igotanoffer.com/blogs/tech/google-data-science-interview

Really good questin: https://towardsdatascience.com/over-100-data-scientist-interview-questions-and-answers-c5a66186769a

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

Write a function to generate N samples from a normal distribution and plot the histogram.

```{r}
x <- rnorm(100)
hist(x)

# what if we want integers - from uniform distribution
y <- runif(100, min = 0, max = 100)
hist(y)

# binomial distrubtion (Bernoulli trial) aka flipipng a coin
# n = number of observations we want to see ex. landing on heads
# size = number of trials per observation
# prob = probability of success for each observation

# Bernoulli distribution
# outcome of 10 coin flips
rbinom(n = 10, size = 1, prob = 0.5)

# Example outcome of 10 flips of 100 coins
rbinom(n = 10, size = 100, prob = 0.5)


# make 150 widgts per day, defective widgets must be reworke, 5% error rate, how many widgets do we need to fix each day this week
rbinom(n = 7, size = 150, prob = 0.05)

# as sample sizes rise, the binomial distribution will start to converge on the normal distribution
```

rbinom - gives approximate times that something will land on X
dbinom - calculates the probabiliyt of getting X success on n binomial trials
pbinom - if we want to calculate the probabiliyt of getting 5 heads OR LESS

```{r}
# fair coin, probability of getting 5 heads in 10 trials
dbinom(x = 5, size = 10, prob = 0.5)
# probabiliyt of getting 5 heads is under 25%
```

Poisson distribution - probability of a number in a fixed interval of time or space (discrete distribution)

For instance, a call center receives an average of 180 calls per hour, 24 hours a day. The calls are independent; receiving one does not change the probability of when the next one will arrive. The number of calls received during any minute has a Poisson probability distribution: the most likely numbers are 2 and 3 but 1 and 4 are also likely and there is a small probability of it being as low as zero and a very small probability it could be 10. 


Normal distribution
- height
- weight
- IQ score

# Statistics and Machine learning

**1) In what situation would you consider mean over median?**

Median over mean
 - when you have outliers or skewed distribution

Mean over median
 - basis for many statistical tests (t-tests, standard deviation)

**2) For sample size n, the margin of error is 3. How many more samples do we need to make the margin of error 0.3?**

ME = CI * sqrt((sd^2)/n)

3 = sqrt(1/n)
9 = 1/n
n = 1/9 = 0.111

0.3 = sqrt(1/n)
0.9 = 1/n
n = 1.111

10x the sample size

3) If you have the numbers 0-100 and pick 2 random numbers, what is the probability that the first number is smaller than the 2nd number

Question to ask
 - are we assuming that we're only picking integers
 - are they randomly picked
 - are they picked with replacement
 - 

4) We have an app that shows photos to users, every photo has a 25% chance of being “bad” what’s the probability that you as a user sees 2 bad photos

Questions
- out of how many photos? or is it 2 bad photos in a row?

**5) If we have n random number generations between 1 and 100 what is the probability of the same number coming up twice?**

1/100 = 1% for first

or we can calculate the probability that they do not come up twice

with 2 numbers = 100/100* 99/100
with 3 numbers = 100/100* 99/00* 98/100

Probability of at least one number cmoing up twice = 1-(P not coming up twice)

**3) What is the assumption of error in linear regression?**

Linear regression null hypothesis
H0: B1 = 0
Ha: B1 != 0

Other assumptions for linear regression
 - relationship between x and y appears linear (scatterplot)
 - there is not relationship between the residuals and the Y variable (plot residuals versus Y - points should be ranodmly scattered)
 - residuals must be normally distributed (residuals must be approximately normally distriubred)
 - variance of the residuals is the same for all values of x (residuals vs. fit plot - must appear as though there is no pattern)