---
title: "Intro_to_purrr"
output: html_document
---

Foundations of Functional Programming with purrr
```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

Read in multiple files
```{r}
files <- list.files()

map(files, read_csv)
```

Find the sum of each elemen of the bird_counts sum list

Maybe the object must be a list?
```{r}
map(bird_counts, sum)
```

The function `map` iterates over a list

`map` traditionally outputs a list

This 
```{r}
map(survey_data, ~nrow(.x))
```

This will output a vector of numbers
```{r}
map_dbl(survey_data, ~nrow(.x))
```

This will output a vector of logicals
```{r}
map_lgl(survey_data, ~nrow(.x) == 14)
```

This will outputs a vector of characters - it will pull out the species names from a list
```{r}
map_chr(species_names, ~.x)
```

This will output a data frame
```{r}
suvey_rows <- data.frame(names = names(survey_data), rows = NA)

survey_rows$rows <- map_dbl(survey_data, ~nrow(.x))

survey_rows 
```

This outputs a list with the name of each movie as the list and the length inside the list
The outputs are the same, but the second is better syntax to use - the .x denotes where the list element goes in the function, when we use ".x" we also have to put a "~" infront of the function
```{r}
map(wesanderson, length)
map(wesanderson, ~length(x))
```


This outputs a dataframe with the number of colors as a column and the rownames as the wesanderson list
```{r}
data.frame(numcolors = map_dbl(wesanderson, ~length(.x)))
```

# Safely, Possibly, and Walk

Can use the function `safely` to show you where errors occurred - when we pipe it into transpose, it will show where the error occurred, first

Replace anything with an error with NA

```{r}
list(-10, 1, 10, 0) %>% 
      map(safely(log, otherwise = NA_real_)) %>%
    # Transpose the result
      transpose()
```

pull out the height element and convert from inches to cm

```{r}
height_ft <- map(sw_people ,"height") %>% 
  map(safely(function(x){
    x * 0.0328084
  }, quiet = FALSE)) %>% 
transpose()
```

replace safely with possibly  - this will out put just the data and not the error messages


```{r}
list(-10, 1, 10, 0) %>% 
      map(safely(function(x) {
log(x)
}
, otherwise = NA_real_)) 
```

use walk() to make lists easier to read - removes double bracketing and makes data more compact


```{r}
Short_list <- list(-10, 1, 10)

Short_list

walk(short_list, print)
```

for plots, you can plot multiple iterations using the map function


```{r}
# Load the gap_split data
data(gap_split)

# Map over the first 10 elements of gap_split
plots <- map2(gap_split[1:10], 
              names(gap_split[1:10]), 
              ~ ggplot(.x, aes(year, lifeExp)) + 
                geom_line() +
                labs(title = "Gap Split"))

# Object name, then function name
walk(plots, print)
```


Check if the list has names
```{r}
names(sw_films)

# if no names, then can use 

sw_films <- sw_films %>%
  set_names(map_chr(sw_films, "title"))
```

These do the same thing
```{r}
# Name gh_users with the names of the users
gh_users_named <- gh_users %>% 
    set_names(map_chr(gh_users, "name"))

# Check gh_repos structure
str(gh_repos)

# Name gh_repos with the names of the repo owner
gh_repos_named <- gh_repos %>% 
    map_chr(~ .[[1]]$owner$login) %>% 
    set_names(gh_repos, .)
```


Sort and try to ask a quesiton
```{r}
# Determine who joined github first
map_chr(gh_users, ~.x[["created_at"]]) %>%
      set_names(map_chr(gh_users, "name")) %>%
    sort()
```

GGplot and dataframes

Pull out data to create 4 columns
```{r}
map_df(gh_users, `[`, 
       c("login","name","followers","public_repos")) 
```

Pull out the title and character names and plot height of characters by film
```{r}
# Turn data into correct dataframe format
film_by_character <- tibble(filmtitle = map_chr(sw_films, "title")) %>%
    mutate(filmtitle, characters = map(sw_films, "characters")) %>%
    unnest()

# Pull out elements from sw_people
sw_characters <- map_df(sw_people, `[`, c("height", "mass", "name", "url"))

# Join the two new objects
character_data <- inner_join(film_by_character, sw_characters, by = c("characters" = "url")) %>%
    # Make sure the columns are numbers
    mutate(height = as.numeric(height), mass = as.numeric(mass))

# Plot the heights, faceted by film title
ggplot(character_data, aes(x = height)) +
  geom_histogram(stat = "count") +
  facet_wrap(~ filmtitle)
```

