---
title: "Intro_to_purrr"
output: html_document
---

Foundations of Functional Programming with purrr
```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

Read in multiple files
```{r}
files <- list.files()

map(files, read_csv)
```

Find the sum of each elemen of the bird_counts sum list

Maybe the object must be a list?
```{r}
map(bird_counts, sum)
```

The function `map` iterates over a list

`map` traditionally outputs a list

This 
```{r}
map(survey_data, ~nrow(.x))
```

This will output a vector of numbers
```{r}
map_dbl(survey_data, ~nrow(.x))
```

This will output a vector of logicals
```{r}
map_lgl(survey_data, ~nrow(.x) == 14)
```

This will outputs a vector of characters - it will pull out the species names from a list
```{r}
map_chr(species_names, ~.x)
```

This will output a data frame
```{r}
suvey_rows <- data.frame(names = names(survey_data), rows = NA)

survey_rows$rows <- map_dbl(survey_data, ~nrow(.x))

survey_rows 
```

This outputs a list with the name of each movie as the list and the length inside the list
The outputs are the same, but the second is better syntax to use - the .x denotes where the list element goes in the function, when we use ".x" we also have to put a "~" infront of the function
```{r}
map(wesanderson, length)
map(wesanderson, ~length(x))
```


This outputs a dataframe with the number of colors as a column and the rownames as the wesanderson list
```{r}
data.frame(numcolors = map_dbl(wesanderson, ~length(.x)))
```

